Archive Your Project

### 2025-01-25 about.qmd
Major rewrite
First explain copyright and licenses,
then practice citation and attribution,
then choose own license.

Create file `copyright.qmd` with material
from `choose_license.qmd` and with
additional information on license conditions
and providing attribution.

Create files `data.qmd` and `code.qmd` with
material from `setup.qmd`. Immediately
cover the citation and attribution.

Relicense `Manuscript.qmd` and all code chunks under CC0 1.0. Relicense other
materials under CC BY-SA 4.0.

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    email: "christoph_scheffel@tu-dresden.de"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

@@

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/). None of the discussion in this tutorial constitutes legal advice.

>>>>

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
bibliography: grateful-refs.bib
---

@@

None of the discussion in this tutorial constitutes legal advice.

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/); the code chunks are also (at your option) available under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/) or the [Apache License\ 2.0](https://www.apache.org/licenses/LICENSE-2.0).

The file `Manuscript.qmd` is made available by Josephine Zerna and Christoph Scheffel under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

### 2025-01-25 archive.qmd
Use APA citation style
Use global language and tidy _quarto.yml
Mention .gitignore files during archival
Major rewrite
First explain copyright and licenses,
then practice citation and attribution,
then choose own license.

Create file `copyright.qmd` with material
from `choose_license.qmd` and with
additional information on license conditions
and providing attribution.

Create files `data.qmd` and `code.qmd` with
material from `setup.qmd`. Immediately
cover the citation and attribution.

Relicense `Manuscript.qmd` and all code chunks under CC0 1.0. Relicense other
materials under CC BY-SA 4.0.

---
title: "Archive Your Project"
lang: "en"
bibliography: literature.bib
---

@@

The project is now ready to be deposited for long-term archival. When considering an appropriate repository, there are a few questions to ponder [excerpt from @Jackson2018, with footnotes removed, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

@@

## Using Zenodo to Archive Your Project

In the following we will demonstrate how to use Zenodo to archive one's project and obtain a DOI.

@@

- __Add/remove files__: To circumvent the file limit on Zenodo, you can bundle your project folder in one ZIP file and upload that instead.
- __Fill in metadata__
  - __Digital Object Identifier__ (DOI): Usually, you will want a DOI, therefore you need to choose _No_ for the question whether you already have a DOI for this upload, and click on _Get a DOI now!_.
  - __Resource type__: Select the most appropriate one, for example, _Publication / Preprint_.
  - __Licenses__: If your project only contains content by you and if you previously only chose one license, you can select that by choosing _Add standard_. Otherwise, click on _Add custom_ and describe how each file is licensed. If you have been using REUSE to record license information, you can run enter `SPDX Document` as title and run the reuse tool with `reuse spdx -o reuse.spdx` to create the file `reuse.spdx`. Then you can paste the content of `reuse.spdx` into the description field of the custom license as it contains information about the license of each file.

If you previously uploaded your project to a public Git repository (which we didn't cover during this tutorial), you could also add the new DOI to your README, for example, under the section "Citation".

>>>>

---
title: "Archive Your Project"
---

@@

The project folder is now ready to be deposited for long-term archival. When considering an appropriate repository, there are a few questions to ponder [excerpt from @Jackson2018, with footnotes removed, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/)]:

@@

## Using Zenodo to Archive Your Project Folder

In the following we will demonstrate how to use Zenodo to archive one's project folder and obtain a DOI.

@@

- __Add/remove files__: To circumvent the file limit on Zenodo, you can bundle your project folder in one ZIP file and upload that instead. Be sure to exclude all files mentioned in your `.gitignore` file!
- __Fill in metadata__
  - __Digital Object Identifier__ (DOI): Usually, you will want a DOI, therefore you need to choose _No_ for the question whether you already have a DOI for this upload, and click on _Get a DOI now!_.
  - __Resource type__: Select the most appropriate one, for example, _Publication / Preprint_.
  - __Licenses__: If your project folder only contains content by you and if you previously only chose one license, you can select that by choosing _Add standard_. Otherwise, click on _Add custom_ and describe how each file is licensed. If you have been using REUSE to record license information, you can run enter `SPDX Document` as title and run the reuse tool with `reuse spdx -o reuse.spdx` to create the file `reuse.spdx`. Then you can paste the content of `reuse.spdx` into the description field of the custom license as it contains information about the license of each file.

If you previously uploaded your project folder to a public Git repository (which we didn't cover during this tutorial), you could also add the new DOI to your README, for example, under the section "Citation".
